### 2018-03-26 tex/paper.tex
Fix typo

Haskell is a pure functional programming language, and uses the \haskellinline{Monad} type class to encapsulate
operations that can potentially have a side effect. Many introductions to monads exist \sjtnote{cite some} but for the 
sake of this discussion it is enough to think of a value of type \haskellinline{m a} where \haskellinline{m} is a monad 
as a ``computation that results in something of type \haskellinline{a}''. The \haskellinline{Monad} API allows 
suchcomputations to be assembled, and then, once assembled, they may be run, in general causing some side-effects as a 
part of the computation.

>>>>

Haskell is a pure functional programming language, and uses the \haskellinline{Monad} type class to encapsulate
operations that can potentially have a side effect. Many introductions to monads exist \sjtnote{cite some} but for the 
sake of this discussion it is enough to think of a value of type \haskellinline{m a} where \haskellinline{m} is a monad 
as a ``computation that results in something of type \haskellinline{a}''. The \haskellinline{Monad} API allows 
such computations to be assembled, and then, once assembled, they may be run, in general causing some side-effects as a 
part of the computation.
